---
title: "Developer guide"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Developer guide}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(gtexr)
```

**WIP**

## Functions

- [ ] Function name is title of endpoint in lower case, with words separated by underscores
- [ ] `@description` section is copied verbatim from API documentation site and ends with a link to the corresponding API endpoint documentation.
- [ ] Further notes may be added under `@details`
- [ ] Arguments 

  - [ ] Names match those for API endpoint, except where the argument accepts an array (vector in R) of values, in which case it is pluralised
  - [ ] Note that the [Get Genomic Features] endpoint takes a path parameter "featureId". The corresponding gtexr argument is prefixed with "." (`.featureId`).
  - [ ] Default values also match those for API endpoint
  - [ ] Query parameters flagged as "required" in the GTEx Portal API documentation do not have default values. Note however that while `variantId` is not flagged as "required" for [Get Linkage Disequilibrium By Variant Data](https://gtexportal.org/api/v2/redoc#tag/Datasets-Endpoints/operation/get_linkage_disequilibrium_by_variant_data_api_v2_dataset_ldByVariant_get), no default value is provided in `get_linkage_disequilibrium_by_variant_data()` as providing `NULL` or an unrecognised variant ID returns an empty response.
  - [ ] Are all documented in `gtexr_arguments.R`. Rules...see also link to separate section(?) (**TO DO**)
  - [ ] All functions therefore use `@inheritParams gtexr_arguments` for documentation
  
- [ ] Use `@family` roxygen tag to match categories on API documentation e.g. ... . This is used to categorise functions on pkgdown site reference page.
- [ ] All return a tibble
- [ ] The first example in `@examples` must produce output, where possible, and be a single function call without assignment (e.g. `get_news_items()`, not `x <- get_news_items()`). This is used to pre-populate argument values in the gtexr shiny app with a working example.
- [ ] All examples should be surrounded by `\dontrun{}`.
- [ ] `gtexr_arguments()` metadata ... (*new section*)

## TODO

- [ ] Complete above documentation
- [ ] Add unit test(s) to enforce above (e.g. check that URL to )
  
